%%=====================================================================================
%%
%%       Filename:  resume.tex
%%
%%    Description:  Zack Parchman's resume
%%
%%        Version:  1.0
%%        Created:  11/17/17
%%       Revision:  none
%%
%%         Author:  Zachary Parchman
%%   Organization:  
%%      Copyright:  Copyright (c) 2017, Zachary Parchman
%%
%%          Notes:  
%%
%%=====================================================================================


\documentclass{res} 
\usepackage{tabularx} 
\usepackage{changepage}
\usepackage{enumitem} 
\usepackage{bibentry}
\usepackage{needspace}


\newcommand{\replaceme}{{\huge{\bf{REPLACE\_ME}}}}
\let\oldSection=\section
\renewcommand{\section}{%
    \filbreak
    \oldSection
}

%#1 = position
%#2 = Date
%#3 = Company
%#4 = Location
%#5 = Description
\newcommand{\job}[5]{ 
\begin{bf}
#3 \hfill #4 \\
#1 \hfill #2 \\
\end{bf}
#5
}

\setlength{\textheight}{10.3in} % Set the length of a page to cause page breaks at convenient locations

%\newenvironment{indentblock}{ \begin{adjustwidth} {\parindent}{4em}
%\hspace{-\parindent}} {\end{adjustwidth}}

\begin{document} 

%for using bibtex without a reference section
\bibliographystyle{plain} \nobibliography{resume}

%magic
\fontsize{10}{11}\selectfont

\begin{resume}

%raise top margin so it fits on one page nicely "setscrew"
\vspace{-25mm}
\begin{center}
    {\bf \Huge Zachary Wayne Parchman}
\end{center}
\vspace{-8mm}
%
%\begin{large}
\begin{small}
    \begin{center}
        Smyrna, TN 37167 $|$
        (615) 668-2543 $|$
        zwparchman@gmail.com $|$
        linkedin thing
        \\
    \end{center}
\end{small}
%\end{large}
\vspace{-8mm}
\rule{\textwidth}{0.4pt}
%
\begin{minipage}[t]{0.45\textwidth}
    \begin{section}{Professional Overview}
        I am experienced working directly with customers and working with
        systems ranging in size from super computers to embedded devices. 
    \end{section}
\end{minipage}
%
\begin{minipage}[t]{0.10\textwidth}
    \hfill
\end{minipage}
%
\begin{minipage}[t]{0.45\textwidth}
    \begin{section}{Impact Snapshot}
        \begin{itemize}
            \item Willing to travel.
            \item Customer interaction experience
            %\item I have created new abstractions to improve productivity
            \item Distributed system experience
        \end{itemize}
    \end{section}
\end{minipage}

\begin{minipage}[t]{0.45\textwidth}
    \begin{section}{Languages}
        \begin{tabularx}{\textwidth}{X X}
            C\# & SQL \\
            C & C++ \\
            Java & Javascript \\
            HTML & CSS \\
            Python 2 and 3 & x86 Assembly \\
            Rust & XML
        \end{tabularx}
    \end{section}
\end{minipage}
%
\begin{minipage}[t]{0.10\textwidth}
    \hfill
\end{minipage}
%
\begin{minipage}[t]{0.45\textwidth}
    \begin{section}{Tools and Libraries}
        \begin{tabularx}{\textwidth}{X X}
            .Net & WPF \\
            MFC & SQL Server \\
            Cuda & MPI \\
            OpenMP & Git \\
            SVN & \LaTeX \\
            Android
        \end{tabularx}
    \end{section}
\end{minipage}
%
\begin{section}{Objective}
    I am looking for a challenging and engaging position that provides opportunities for advancement.
\end{section}
%
\section{Experience}
\job{Software Developer} 
{April 2018 - Present} 
{Quality Manufacturing Systems Incorporated}
{La Vergne, Tennessee}
{
    I have designed and implement database driven software for automated
    pharmacies. This software includes real time  control software, web
    services, and applications used by the line workers.  
}

\job{Research Programmer Intern} 
{May 2015 - May 2017} 
{Oak Ridge National Laboratory / ORISE} 
{Oak Ridge, Tennessee}
{
    I designed and implemented a new programming model for heterogeneous large scale systems as part of a team.
    This effort resulted in multiple scientific papers. One of the
    more interesting parts was a distributed memory hash table that utilized
    hardware RDMA and remote atomic operations to implement distributed mutexes.
}

\job{Research Programmer Intern} 
{May 2015 - August 2015}
{Oak Ridge National Laboratory / ORISE}
{Oak Ridge, Tennessee}
{
    I planned and executed the conversion of benchmarking programs to use an
    experimental modification to MPI to allow for fault tolerance.
}

\job{Teacher's Assistant} {January 2014 - May 2016}
{Tennessee Technological University}
{Cookeville, Tennessee}
{
    I graded and tutored for computer science classes to assist a professor in
    college courses.
}

\begin{section}{Education}
    {\bf Bachelor of Science in Computer Science, December 2013}\\
    Tennessee Technological University, Cookeville, Tennessee\\
    Graduated with a GPA of 3.08 on a 4.0 scale \\
    The classes taken include:\\
        \begin{tabularx}{\textwidth}{@{} X X X}
            Networking & High Performance Computing & Artificial Intelligence \\
            Programming Languages & Internet Security & Parallel Programming  \\
        \end{tabularx}
\end{section}

\begin{section}{Publications}
Zachary W. Parchman, Ferrol Aderholdt, and Manjunath Gorentla Venkata. {\bf Sharp hash: A high-
performing distributed hash for extreme-scale systems.} In 2017 IEEE International Conference on
Cluster Computing, CLUSTER 2017, Honolulu, HI, USA, September 5-8, 2017, pages 647-648, 2017

Manjunath Gorentla Venkata, Ferrol Aderholdt, and Zachary W. Parchman. {\bf Sharp: Towards program-
ming extreme-scale systems with hierarchical heterogeneous memory.} In 46th International Conference
on Parallel Processing Workshops, ICPP Workshops 2017, Bristol, United Kingdom, August 14-17,
2017, pages 145-154, 2017

F. Aderholdt, M. G. Venkata, and Z. Parchman. {\bf Sharp data constructs: Data constructs to enable
data-centric computing.} In 2018 26th Euromicro International Conference on Parallel, Distributed and
Network-based Processing (PDP), pages 170-177, March 2018


Zachary W. Parchman, Geoffroy Vallée, Thomas Naughton, Christian Engelmann, David E. Bernholdt,
and Stephen L. Scott. {\bf Adding fault tolerance to NPB benchmarks using ULFM.} In Proceedings of
the ACM Workshop on Fault-Tolerance for HPC at Extreme Scale, FTXS@HPDC 2016, Kyoto, Japan,
May 31, 2016, pages 27-34, 2016
\end{section}

%I'll do this right by modifying the bibtext... eventually
%\bibentry{DBLP:conf/cluster/ParchmanAV17}

%\bibentry{DBLP:conf/icppw/VenkataAP17}

%\bibentry{DBLP:conf/hpdc/ParchmanVNEBS16}

%\bibentry{DBLP:conf/eicpdnp/AderholdDataConstructs}

%\section{References}
%\vspace{2mm}
%\begin{tabularx}{\textwidth}{X X}
%Dr. Thomas Naughton  & Dr. Manjunath Venkata \\
%Research staff & Research staff \\
%UT-Battelle / Oak Ridge National Laboratory & UT-Battelle / Oak Ridge National Laboratory \\
%(865) 576-4184 & (865) 574-5949 \\
%naughtont@ornl.gov & manjugv@ornl.gov \\
%Relationship: Mentor for 2015 internship & Relationship: Mentor for 2016 internship
%\end{tabularx}
%
\end{resume}
\end{document}
